Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-08-10 Tex/Paper.tex
Updated plots
Added transverse phasespace plots

\begin{figure*}[hbt]
    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittance}
    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
        an on-axis beam with respect to the drive beam axis (left) and an offset beam (right) with an offset of one
        $\sigma_{x}$ in the x plane. The moving window for emittance calculation is longitudinal slices of
        $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than $100$ macro
        particles have been included, which accounts for the abrupt edge as well as the noise at either end of the beam
        due to low statistics. The blue lines show the peak electron beam density profile. For reference, the plasma 
        density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid lines are at
        the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after $40\unit{m}$, and
        the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the witness beam, these
        simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which causes the
        structure to brake down after about $50\unit{m}$.}
\end{figure*}

The witness beam's self-generated bubble prevents the tailing end of the beam to see any measurable emittance growth.
For the majority of the cases we studied that maintained a stable accelerating structure, about $70\%$ of the beam
retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows the $100\unit{pC}$ and $\sigma_{z} = 60\unit{\mu m}$
case extended to a $100\unit{m}$ plasma case and the drive beam energy increased to $7\unit{TeV}$ (LHC energy) to
prevent dephasing, which for the SPS beam case starts to become significant after about $50\unit{m}$.

The on-axis density of the electron beam increases as its gamma factor increases and its transverse size decreases. The
beam radius follows the matched beam equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$.

@@

>>>>

\begin{figure*}[hbt]
    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittance}
    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
        an on-axis beam with respect to the drive beam axis (left) and an offset beam (right) with an offset of one
        $\sigma_{x} = 5.24\unit{\mu m}$ in the x plane. The moving window for emittance calculation is longitudinal
        slices of $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
        $100$ macro particles have been included, which accounts for the abrupt edge as well as the noise at either end
        of the beam due to low statistics. The blue lines show the peak electron beam density profile. For reference,
        the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid
        lines are at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after
        $40\unit{m}$, and the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the
        witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which
        causes the structure to brake down after about $50\unit{m}$.}
\end{figure*}

The witness beam's self-generated bubble prevents the tailing end of the beam to see any measurable emittance growth.
For the majority of the cases we studied that maintained a stable accelerating structure, about $70-80\%$ of the beam
retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows the $100\unit{pC}$ and $\sigma_{z} = 60\unit{\mu m}$
case extended to a $100\unit{m}$ plasma and the drive beam energy increased to $7\unit{TeV}$ (LHC energy) to prevent
dephasing. Dephasing for the SPS beam case starts to become significant after about $50\unit{m}$.

The on-axis density of the electron beam increases as its gamma factor increases and its transverse size decreases. The
beam radius follows the evolution given by equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$ for the section
of the beam where normalised emittance is preserved.

@@

\begin{figure*}[hbt]
    \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
    \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
    \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
    \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
    \\
    \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
    \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
    \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
    \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
        plasma position. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
        particles and lines represent particles with position $1.40 < \xi < 1.42$. The red particles and lines
        represent particles with position $1.55 < \xi < 1.57$.}
\end{figure*}

Our configuration shows robustness to electron beam transverse offset as the bubble generated by the witness beam
wakefield follows the beam. The head of the beam does not benefit from this, and we see some defocusing in this region.
However, since this the proton wakefield creates a quasi linear condition, we still see the head of the beam
stabilising. The off-axis case has a larger initial emittance growth, but the growth levels off after the first few
metres and stays constant for the remainder of the plasma accelerator section.
